---
title: "Tutorial"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
library(mosaic)
library(ggformula)
knitr::opts_chunk$set(echo = FALSE)
mod_of_hp <- lm(hp ~ cyl +disp , data = mtcars)

```


## Simulation

What are the outcomes of adding up n dice?


This command throws three dice and reports the values. Change it to throw 10 dice.

Make a model of hp
```{r unique_name, exercise = TRUE}
mod <- lm(hp ~ cyl +disp , data = mtcars)
```

```{r unique_name-hint}
size = 10
```

```{r unique_name-hint2}
replace = TRUE
```

```{r unique_name-solution}
sample(1:6, size = 10, replace = TRUE)
```

A model of horsepower is contained in `mod_of_hp`. Use that to find the confidence interval on disp
```{r second-block, exercise = TRUE}

```



### Quiz

*You can include any number of single or multiple choice questions as a quiz. Use the `question` function to define a question and the `quiz` function for grouping multiple questions together.*

Some questions to verify that you understand the purposes of various base and recommended R packages:

```{r quiz}
quiz(
  question("Which package contains functions for installing other R packages?",
    answer("base"),
    answer("tools"),
    answer("utils", correct = TRUE),
    answer("codetools")
  ),
  question("Which of the R packages listed below are used to create plots?",
    answer("lattice", correct = TRUE),
    answer("tools"),
    answer("stats"),
    answer("grid", correct = TRUE)
  )
)
```

